Global study of well-being and internet adoption | Online analysis supplement

### 2022-05-16 index.Rmd
Cleaning

Welcome! This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).

::: {.callout-note}
### How to reproduce our results

@@

::: {.callout-important}
The project repo includes the GBD and ITU datasets, and **a synthetic mock version of the GWP dataset** to enable reproducing all our computations.
**The models take several hours/days each to run**---depending on your local computing resources---and therefore the rendering process can take several days. For this reason it might be easier to run the individual `.Rmd` files interactively in RStudio.
:::

If something doesn't work please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).
:::

>>>>

Welcome! This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [submitted]()). It contains all the analyses reported in the manuscript along with supplemental figures and data. The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).

### How to reproduce our results

@@

If you encounter problems, please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).

::: {.callout-important}
The project repo includes the GBD and ITU datasets, and a synthetic mock version of the GWP dataset to enable reproducing all our computations.
**The models take several hours/days each to run**---depending on your local computing resources---and therefore the rendering process can take several days. For this reason, the build will fail after having cleaned the data. Then, run `models.R` with settings specific to your environment/cluster. Once that is done you can build again and it should work.
:::
